Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-02-10 paper/letter.tex
rotation+outflow appendix

>>>>

\section*{Joint Effect of Rotation and Outflow}

The almost complete absence of outflows is a central requirement for
reproducing the lyman alpha line in \tol. In this section we present
some results on the exploration of the presence of outflows join with
the bulk rotation. We defer a detailed exploration of this effects for
another publication.

Figure XX shows the results of four different models. a) pure rotation
($V_{\rm rot}=100$ km s$^{-1}$), b) pure outflow ($V_{\rm out}=100$ km
s$^{-1}$), c) mixed outflow with rotation ($V_{\rm rot}=100$ km s$^{-1}$)($V_{\rm rot}=25$ km s$^{-1}$).
